<!-- R Commander Markdown Template -->

Replace with Main Title
=======================

### Savanna

### `r as.character(Sys.Date())`

```{r echo=FALSE}
# include this code chunk as-is to set options
knitr::opts_chunk$set(comment=NA, prompt=TRUE, out.width=750, fig.height=8, fig.width=8)
library(Rcmdr)
library(car)
library(RcmdrMisc)
```
## Please modify this section of the code to change to your own directory. Make absolutely sure that you have all 
#of the relevant associated data files in your directory as well.

```{r}
setwd("C:/Users/Savanna/Documents/1NewRDirectory")
```

#Loading Fallin Data#


```{r}
FallinPlantSpecies <- read.csv("FallinPlantSpecies.csv")
```


```{r}
str(FallinPlantSpecies)
```


```{r}
FallinPlantChemistry <- read.csv("FallinPlantChemistry.csv")
```


```{r}
str(FallinPlantChemistry)
```

#Converting both files into dataframes for analyses#

```{r}
FallinPlantSpecies1 <- data.frame(FallinPlantSpecies)
```


```{r}
FallinPlantChemistry1 <- data.frame(FallinPlantChemistry)
```

#Now to run several similar analyses to determine biodiversity levels in different concentrations of specific elements,
#as well as in different pH levels.

```{r}
FallinPlantChemistry1$Al2O3 <- as.factor(FallinPlantChemistry1$Al2O3)
```


```{r}
Fallin.Al2O3 <- renyicomp(FallinPlantSpecies1, y=FallinPlantChemistry1, factor = 'Al2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Fallin.Al2O3)
```


```{r}
Fallin.Al2O3
```


```{r}
FallinPlantChemistry1$Fe2O3 <- as.factor(FallinPlantChemistry1$Fe2O3)
```


```{r}
Fallin.Fe2O3 <- renyicomp(FallinPlantSpecies1, y=FallinPlantChemistry1, factor = 'Fe2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Fallin.Fe2O3)
```


```{r}
Fallin.Fe2O3
```


```{r}
FallinPlantChemistry1$CaO <- as.factor(FallinPlantChemistry1$CaO)
```


```{r}
Fallin.CaO <- renyicomp(FallinPlantSpecies1, y=FallinPlantChemistry1, factor = 'CaO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Fallin.CaO)
```


```{r}
Fallin.CaO
```


```{r}
FallinPlantChemistry1$MgO <- as.factor(FallinPlantChemistry1$MgO)
```


```{r}
Fallin.MgO <- renyicomp(FallinPlantSpecies1, y=FallinPlantChemistry1, factor = 'MgO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Fallin.MgO)
```


```{r}
Fallin.MgO
```


```{r}
FallinPlantChemistry1$Na2O <- as.factor(FallinPlantChemistry1$Na2O)
```


```{r}
Fallin.Na2O <- renyicomp(FallinPlantSpecies1, y=FallinPlantChemistry1, factor = 'Na2O',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Fallin.Na2O)
```


```{r}
Fallin.Na2O
```


```{r}
FallinPlantChemistry1$K2O <- as.factor(FallinPlantChemistry1$K2O)
```


```{r}
Fallin.K2O <- renyicomp(FallinPlantSpecies1, y=FallinPlantChemistry1, factor = 'K2O',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Fallin.K2O)
```


```{r}
Fallin.K2O
```


```{r}
FallinPlantChemistry1$Cr2O3 <- as.factor(FallinPlantChemistry1$Cr2O3)
```


```{r}
Fallin.Cr2O3 <- renyicomp(FallinPlantSpecies1, y=FallinPlantChemistry1, factor = 'Cr2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Fallin.Cr2O3)
```


```{r}
Fallin.Cr2O3
```


```{r}
FallinPlantChemistry1$TiO2 <- as.factor(FallinPlantChemistry1$TiO2)
```


```{r}
Fallin.TiO2 <- renyicomp(FallinPlantSpecies1, y=FallinPlantChemistry1, factor = 'TiO2',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Fallin.TiO2)
```


```{r}
Fallin.TiO2
```


```{r}
FallinPlantChemistry1$MnO <- as.factor(FallinPlantChemistry1$MnO)
```


```{r}
Fallin.MnO <- renyicomp(FallinPlantSpecies1, y=FallinPlantChemistry1, factor = 'MnO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Fallin.MnO)
```


```{r}
Fallin.MnO
```


```{r}
FallinPlantChemistry1$P2O5 <- as.factor(FallinPlantChemistry1$P2O5)
```


```{r}
Fallin.P2O5 <- renyicomp(FallinPlantSpecies1, y=FallinPlantChemistry1, factor = 'P2O5',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Fallin.P2O5)
```


```{r}
Fallin.P2O5
```


```{r}
FallinPlantChemistry1$SrO <- as.factor(FallinPlantChemistry1$SrO)
```


```{r}
Fallin.SrO <- renyicomp(FallinPlantSpecies1, y=FallinPlantChemistry1, factor = 'SrO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Fallin.SrO)
```


```{r}
Fallin.SrO
```


```{r}
FallinPlantChemistry1$BaO <- as.factor(FallinPlantChemistry1$BaO)
```


```{r}
Fallin.BaO <- renyicomp(FallinPlantSpecies1, y=FallinPlantChemistry1, factor = 'BaO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Fallin.BaO)
```


```{r}
Fallin.BaO
```


```{r}
FallinPlantChemistry1$As <- as.factor(FallinPlantChemistry1$As)
```


```{r}
Fallin.As <- renyicomp(FallinPlantSpecies1, y=FallinPlantChemistry1, factor = 'As',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Fallin.As)
```


```{r}
Fallin.As
```


```{r}
FallinPlantChemistry1$Co <- as.factor(FallinPlantChemistry1$Co)
```


```{r}
Fallin.Co <- renyicomp(FallinPlantSpecies1, y=FallinPlantChemistry1, factor = 'Co',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Fallin.Co)
```


```{r}
Fallin.Co
```


```{r}
FallinPlantChemistry1$Pb <- as.factor(FallinPlantChemistry1$Pb)
```


```{r}
Fallin.Pb <- renyicomp(FallinPlantSpecies1, y=FallinPlantChemistry1, factor = 'Pb',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Fallin.Pb)
```


```{r}
Fallin.Pb
```


```{r}
FallinPlantChemistry1$S <- as.factor(FallinPlantChemistry1$S)
```


```{r}
Fallin.S <- renyicomp(FallinPlantSpecies1, y=FallinPlantChemistry1, factor = 'S',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Fallin.S)
```


```{r}
Fallin.S
```


```{r}
FallinPlantChemistry1$V <- as.factor(FallinPlantChemistry1$V)
```


```{r}
Fallin.V <- renyicomp(FallinPlantSpecies1, y=FallinPlantChemistry1, factor = 'V',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Fallin.V)
```


```{r}
Fallin.V
```
#Loading Addiewell Bing Data#

```{r}
AddiewellPlantChemistry <- read.csv("AddiewellPlantChemistry.csv")
```


```{r}
str(AddiewellPlantChemistry)
```

```{r}
AddiewellPlantChemistry1 <- data.frame(AddiewellPlantChemistry)
```


```{r}
AddiewellPlantSpecies <- read.csv("AddiewellPlantSpecies.csv")
```


```{r}
str(AddiewellPlantSpecies)
```
#Converting Addiewell data to dataframes for analyses#

```{r}
AddiewellPlantSpecies1 <- data.frame(AddiewellPlantSpecies)
```


```{r}
AddiewellPlantChemistry1 <- data.frame(AddiewellPlantChemistry)
```

#Running the first of several analyses to determine biodiversity levels in different concentrations of specific elements,
#as well as in different pH levels.

```{r}
AddiewellPlantChemistry1$pH_level <- as.factor(AddiewellPlantChemistry1$pH_level)
```


```{r}
Addiewell.pH <- renyicomp(FallinPlantSpecies1, y=AddiewellPlantChemistry1, factor = 'pH_level',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Addiewell.pH)
```

```{r}
Addiewell.pH
```


```{r}
AddiewellPlantChemistry1$SiO2 <- as.factor(AddiewellPlantChemistry1$SiO2)
```


```{r}
Addiewell.SiO2 <- renyicomp(FallinPlantSpecies1, y=AddiewellPlantChemistry1, factor = 'SiO2',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Addiewell.SiO2)
```


```{r}
Addiewell.SiO2
```


```{r}
AddiewellPlantChemistry1$Al2O3 <- as.factor(AddiewellPlantChemistry1$Al2O3)
```


```{r}
Addiewell.Al2O3 <- renyicomp(FallinPlantSpecies1, y=AddiewellPlantChemistry1, factor = 'Al2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Addiewell.Al2O3)
```


```{r}
Addiewell.Al2O3
```


```{r}
AddiewellPlantChemistry1$Fe2O3 <- as.factor(AddiewellPlantChemistry1$Fe2O3)
```


```{r}
Addiewell.Fe2O3 <- renyicomp(FallinPlantSpecies1, y=AddiewellPlantChemistry1, factor = 'Fe2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Addiewell.Fe2O3)
```


```{r}
Addiewell.Fe2O3
```


```{r}
AddiewellPlantChemistry1$CaO <- as.factor(AddiewellPlantChemistry1$CaO)
```


```{r}
Addiewell.CaO <- renyicomp(FallinPlantSpecies1, y=AddiewellPlantChemistry1, factor = 'CaO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Addiewell.CaO)
```


```{r}
Addiewell.CaO
```


```{r}
AddiewellPlantChemistry1$MgO <- as.factor(AddiewellPlantChemistry1$MgO)
```


```{r}
Addiewell.MgO <- renyicomp(FallinPlantSpecies1, y=AddiewellPlantChemistry1, factor = 'MgO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Addiewell.MgO)
```


```{r}
Addiewell.MgO
```


```{r}
AddiewellPlantChemistry1$Na2O <- as.factor(AddiewellPlantChemistry1$Na2O)
```


```{r}
Addiewell.Na2O <- renyicomp(FallinPlantSpecies1, y=AddiewellPlantChemistry1, factor = 'Na2O',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Addiewell.Na2O)
```


```{r}
Addiewell.Na2O
```


```{r}
AddiewellPlantChemistry1$K2O <- as.factor(AddiewellPlantChemistry1$K2O)
```


```{r}
Addiewell.K2O <- renyicomp(FallinPlantSpecies1, y=AddiewellPlantChemistry1, factor = 'K2O',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Addiewell.K2O)
```


```{r}
Addiewell.K2O
```


```{r}
AddiewellPlantChemistry1$Cr2O3 <- as.factor(AddiewellPlantChemistry1$Cr2O3)
```


```{r}
Addiewell.Cr2O3 <- renyicomp(FallinPlantSpecies1, y=AddiewellPlantChemistry1, factor = 'Cr2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Addiewell.Cr2O3)
```


```{r}
Addiewell.Cr2O3
```


```{r}
AddiewellPlantChemistry1$TiO2 <- as.factor(AddiewellPlantChemistry1$TiO2)
```


```{r}
Addiewell.TiO2 <- renyicomp(FallinPlantSpecies1, y=AddiewellPlantChemistry1, factor = 'TiO2',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Addiewell.TiO2)
```


```{r}
Addiewell.TiO2
```


```{r}
AddiewellPlantChemistry1$MnO <- as.factor(AddiewellPlantChemistry1$MnO)
```


```{r}
Addiewell.MnO <- renyicomp(FallinPlantSpecies1, y=AddiewellPlantChemistry1, factor = 'MnO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Addiewell.MnO)
```


```{r}
Addiewell.MnO
```


```{r}
AddiewellPlantChemistry1$P2O5 <- as.factor(AddiewellPlantChemistry1$P2O5)
```


```{r}
Addiewell.P2O5 <- renyicomp(FallinPlantSpecies1, y=AddiewellPlantChemistry1, factor = 'P2O5',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Addiewell.P2O5)
```


```{r}
Addiewell.P2O5
```


```{r}
AddiewellPlantChemistry1$SrO <- as.factor(AddiewellPlantChemistry1$SrO)
```


```{r}
Addiewell.SrO <- renyicomp(FallinPlantSpecies1, y=AddiewellPlantChemistry1, factor = 'SrO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Addiewell.SrO)
```


```{r}
Addiewell.SrO
```


```{r}
AddiewellPlantChemistry1$BaO <- as.factor(AddiewellPlantChemistry1$BaO)
```


```{r}
Addiewell.BaO <- renyicomp(FallinPlantSpecies1, y=AddiewellPlantChemistry1, factor = 'BaO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Addiewell.BaO)
```


```{r}
Addiewell.BaO
```


```{r}
AddiewellPlantChemistry1$As <- as.factor(AddiewellPlantChemistry1$As)
```


```{r}
Addiewell.As <- renyicomp(FallinPlantSpecies1, y=AddiewellPlantChemistry1, factor = 'As',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Addiewell.As)
```


```{r}
Addiewell.As
```


```{r}
AddiewellPlantChemistry1$Co <- as.factor(AddiewellPlantChemistry1$Co)
```


```{r}
Addiewell.Co <- renyicomp(FallinPlantSpecies1, y=AddiewellPlantChemistry1, factor = 'Co',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Addiewell.Co)
```


```{r}
Addiewell.Co
```


```{r}
AddiewellPlantChemistry1$Pb <- as.factor(AddiewellPlantChemistry1$Pb)
```


```{r}
Addiewell.Pb <- renyicomp(FallinPlantSpecies1, y=AddiewellPlantChemistry1, factor = 'Pb',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Addiewell.Pb)
```


```{r}
Addiewell.Pb
```


```{r}
AddiewellPlantChemistry1$S <- as.factor(AddiewellPlantChemistry1$S)
```


```{r}
Addiewell.S <- renyicomp(FallinPlantSpecies1, y=AddiewellPlantChemistry1, factor = 'S',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Addiewell.S)
```


```{r}
Addiewell.S
```


```{r}
AddiewellPlantChemistry1$V <- as.factor(AddiewellPlantChemistry1$V)
```


```{r}
Addiewell.V <- renyicomp(FallinPlantSpecies1, y=AddiewellPlantChemistry1, factor = 'V',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Addiewell.V)
```


```{r}
Addiewell.V
```

#Loading Penicuik Data#

```{r}
PenicuikPlantSpecies <- read.csv("PenicuikPlantSpecies.csv")
```

```{r}
str(PenicuikPlantSpecies)
```

```{r}
PenicuikPlantChemistry <- read.csv("PenicuikPlantChemistry.csv")
```

```{r}
str(PenicuikPlantChemistry)
```

#Converting the Penicuik Data into dataframes for analyses

```{r}
PenicuikPlantSpecies1 <- data.frame(PenicuikPlantSpecies)
```

```{r}
PenicuikPlantChemistry1 <- data.frame(PenicuikPlantChemistry)
```

#Running the first of several analyses to determine biodiversity levels in different concentrations of specific elements,
#as well as in different pH levels.

```{r}
PenicuikPlantChemistry1$pH_level <- as.factor(PenicuikPlantChemistry1$pH_level)
```


```{r}
Penicuik.pH <- renyicomp(FallinPlantSpecies1, y=PenicuikPlantChemistry1, factor = 'pH_level',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
Penicuik.pH <- renyicomp(FallinPlantSpecies1, y=PenicuikPlantChemistry1, factor = 'pH_level',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
PenicuikPlantChemistry1$pH_level <- as.factor(PenicuikPlantChemistry1$pH_level)
```


```{r}
Penicuik.pH <- renyicomp(FallinPlantSpecies1, y=PenicuikPlantChemistry1, factor = 'pH_level',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Penicuik.pH)
```


```{r}
Penicuik.pH
```


```{r}
PenicuikPlantChemistry1$SiO2 <- as.factor(PenicuikPlantChemistry1$SiO2)
```


```{r}
Penicuik.SiO2 <- renyicomp(FallinPlantSpecies1, y=PenicuikPlantChemistry1, factor = 'SiO2',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Penicuik.SiO2)
```


```{r}
Penicuik.SiO2
```


```{r}
PenicuikPlantChemistry1$Al2O3 <- as.factor(PenicuikPlantChemistry1$Al2O3)
```


```{r}
Penicuik.Al2O3 <- renyicomp(FallinPlantSpecies1, y=PenicuikPlantChemistry1, factor = 'Al2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Penicuik.Al2O3)
```


```{r}
Penicuik.Al2O3
```


```{r}
PenicuikPlantChemistry1$Fe2O3 <- as.factor(PenicuikPlantChemistry1$Fe2O3)
```


```{r}
Penicuik.Fe2O3 <- renyicomp(FallinPlantSpecies1, y=PenicuikPlantChemistry1, factor = 'Fe2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Penicuik.Fe2O3)
```


```{r}
Penicuik.Fe2O3
```


```{r}
PenicuikPlantChemistry1$CaO <- as.factor(PenicuikPlantChemistry1$CaO)
```


```{r}
Penicuik.CaO <- renyicomp(FallinPlantSpecies1, y=PenicuikPlantChemistry1, factor = 'CaO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Penicuik.CaO)
```


```{r}
Penicuik.CaO
```


```{r}
PenicuikPlantChemistry1$MgO <- as.factor(PenicuikPlantChemistry1$MgO)
```


```{r}
Penicuik.MgO <- renyicomp(FallinPlantSpecies1, y=PenicuikPlantChemistry1, factor = 'MgO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Penicuik.MgO)
```


```{r}
Penicuik.MgO
```


```{r}
PenicuikPlantChemistry1$Na2O <- as.factor(PenicuikPlantChemistry1$Na2O)
```


```{r}
Penicuik.Na2O <- renyicomp(FallinPlantSpecies1, y=PenicuikPlantChemistry1, factor = 'Na2O',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Penicuik.Na2O)
```


```{r}
Penicuik.Na2O
```


```{r}
PenicuikPlantChemistry1$K2O <- as.factor(PenicuikPlantChemistry1$K2O)
```


```{r}
Penicuik.K2O <- renyicomp(FallinPlantSpecies1, y=PenicuikPlantChemistry1, factor = 'K2O',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Penicuik.K2O)
```


```{r}
Penicuik.K2O
```


```{r}
PenicuikPlantChemistry1$Cr2O3 <- as.factor(PenicuikPlantChemistry1$Cr2O3)
```


```{r}
Penicuik.Cr2O3 <- renyicomp(FallinPlantSpecies1, y=PenicuikPlantChemistry1, factor = 'Cr2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Penicuik.Cr2O3)
```


```{r}
Penicuik.Cr2O3
```


```{r}
PenicuikPlantChemistry1$TiO2 <- as.factor(PenicuikPlantChemistry1$TiO2)
```


```{r}
Penicuik.TiO2 <- renyicomp(FallinPlantSpecies1, y=PenicuikPlantChemistry1, factor = 'TiO2',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Penicuik.TiO2)
```


```{r}
Penicuik.TiO2
```


```{r}
PenicuikPlantChemistry1$MnO <- as.factor(PenicuikPlantChemistry1$MnO)
```


```{r}
Penicuik.MnO <- renyicomp(FallinPlantSpecies1, y=PenicuikPlantChemistry1, factor = 'MnO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Penicuik.MnO)
```


```{r}
Penicuik.MnO
```


```{r}
PenicuikPlantChemistry1$P2O5 <- as.factor(PenicuikPlantChemistry1$P2O5)
```


```{r}
Penicuik.P2O5 <- renyicomp(FallinPlantSpecies1, y=PenicuikPlantChemistry1, factor = 'P2O5',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Penicuik.P2O5)
```


```{r}
Penicuik.P2O5
```


```{r}
PenicuikPlantChemistry1$SrO <- as.factor(PenicuikPlantChemistry1$SrO)
```


```{r}
Penicuik.SrO <- renyicomp(FallinPlantSpecies1, y=PenicuikPlantChemistry1, factor = 'SrO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Penicuik.SrO)
```


```{r}
Penicuik.SrO
```


```{r}
PenicuikPlantChemistry1$BaO <- as.factor(PenicuikPlantChemistry1$BaO)
```


```{r}
Penicuik.BaO <- renyicomp(FallinPlantSpecies1, y=PenicuikPlantChemistry1, factor = 'BaO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Penicuik.BaO)
```


```{r}
Penicuik.BaO
```

```{r}
PenicuikPlantChemistry1$As <- as.factor(PenicuikPlantChemistry1$As)
```


```{r}
Penicuik.As <- renyicomp(FallinPlantSpecies1, y=PenicuikPlantChemistry1, factor = 'As',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Penicuik.As)
```


```{r}
Penicuik.As
```


```{r}
PenicuikPlantChemistry1$Co <- as.factor(PenicuikPlantChemistry1$Co)
```


```{r}
Penicuik.Co <- renyicomp(FallinPlantSpecies1, y=PenicuikPlantChemistry1, factor = 'Co',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Penicuik.Co)
```


```{r}
Penicuik.Co
```


```{r}
PenicuikPlantChemistry1$Pb <- as.factor(PenicuikPlantChemistry1$Pb)
```


```{r}
Penicuik.Pb <- renyicomp(FallinPlantSpecies1, y=PenicuikPlantChemistry1, factor = 'Pb',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Penicuik.Pb)
```


```{r}
Penicuik.Pb
```


```{r}
PenicuikPlantChemistry1$S <- as.factor(PenicuikPlantChemistry1$S)
```


```{r}
Penicuik.S <- renyicomp(FallinPlantSpecies1, y=PenicuikPlantChemistry1, factor = 'S',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Penicuik.S)
```


```{r}
Penicuik.S
```


```{r}
PenicuikPlantChemistry1$V <- as.factor(PenicuikPlantChemistry1$V)
```


```{r}
Penicuik.V <- renyicomp(FallinPlantSpecies1, y=PenicuikPlantChemistry1, factor = 'V',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```


```{r}
summary(Penicuik.V)
```


```{r}
Penicuik.V
```

```{r}
BarrowPlantSpecies <- read.csv("BarrowPlantSpecies.csv")
```


```{r}
str(BarrowPlantSpecies)
```

```{r}
BarrowPlantChemistry <- read.csv("BarrowPlantChemistry.csv")
```


```{r}
str(BarrowPlantChemistry)
```

#Converting to dataframes for analyses

```{r}
BarrowPlantSpecies1 <- data.frame(BarrowPlantSpecies)
```

```{r}
BarrowPlantChemistry1 <- data.frame(BarrowPlantChemistry)
```

#Running the first of several analyses to determine biodiversity levels in different concentrations of specific elements,
#as well as in different pH levels for the Barrow data

```{r}
BarrowPlantChemistry1$pH_level <- as.factor(BarrowPlantChemistry1$pH_level)
```


```{r}
Barrow.pH <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'pH_level',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.pH)
```

```{r}
Barrow.pH
```

```{r}
BarrowPlantChemistry1$Al2O3 <- as.factor(BarrowPlantChemistry1$Al2O3)
```


```{r}
BarrowAl2O3 <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'Al2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(BarrowAl2O3)
```

```{r}
BarrowAl2O3
```

```{r}
BarrowPlantChemistry1$MgO <- as.factor(BarrowPlantChemistry1$MgO)
```


```{r}
Barrow.MgO <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'MgO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.MgO)
```

```{r}
Barrow.MgO
```


```{r}
BarrowPlantChemistry1$CaO <- as.factor(BarrowPlantChemistry1$CaO)
```

```{r}
Barrow.CaO <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'CaO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.CaO)
```

```{r}
Barrow.CaO
```

```{r}
BarrowPlantChemistry1$Fe2O3 <- as.factor(BarrowPlantChemistry1$Fe2O3)
```

```{r}
Barrow.Fe2O3 <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'Fe2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.Fe2O3)
```

```{r}
Barrow.Fe2O3
```

```{r}
BarrowPlantChemistry1$Na2O <- as.factor(BarrowPlantChemistry1$Na2O)
```

```{r}
Barrow.Na2O <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'Na2O',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.Na2O)
```

```{r}
Barrow.Na2O
```

```{r}
BarrowPlantChemistry1$K2O <- as.factor(BarrowPlantChemistry1$K2O)
```

```{r}
Barrow.K2O <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'K2O',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.K2O)
```

```{r}
Barrow.K2O
```

```{r}
BarrowPlantChemistry1$Cr2O3 <- as.factor(BarrowPlantChemistry1$Cr2O3)
```

```{r}
Barrow.Cr2O3 <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'Cr2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.Cr2O3)
```

```{r}
Barrow.Cr2O3
```

```{r}
BarrowPlantChemistry1$TiO2 <- as.factor(BarrowPlantChemistry1$TiO2)
```

```{r}
Barrow.TiO2 <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'TiO2',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.TiO2)
```

```{r}
Barrow.TiO2
```

```{r}
BarrowPlantChemistry1$MnO <- as.factor(BarrowPlantChemistry1$MnO)
```

```{r}
Barrow.MnO <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'MnO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.MnO)
```

```{r}
Barrow.MnO
```

```{r}
BarrowPlantChemistry1$P2O5 <- as.factor(BarrowPlantChemistry1$P2O5)
```

```{r}
Barrow.P2O5 <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'P2O5',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.P2O5)
```

```{r}
Barrow.P2O5
```

```{r}
BarrowPlantChemistry1$SrO <- as.factor(BarrowPlantChemistry1$SrO)
```

```{r}
Barrow.SrO <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'SrO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.SrO)
```

```{r}
Barrow.SrO
```

```{r}
BarrowPlantChemistry1$BaO <- as.factor(BarrowPlantChemistry1$BaO)
```

```{r}
Barrow.BaO <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'BaO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.BaO)
```

```{r}
Barrow.BaO
```


```{r}
BarrowPlantChemistry1$As <- as.factor(BarrowPlantChemistry1$As)
```

```{r}
Barrow.As <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'As',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.As)
```

```{r}
Barrow.As
```

```{r}
BarrowPlantChemistry1$Co <- as.factor(BarrowPlantChemistry1$Co)
```

```{r}
Barrow.Co <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'Co',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.Co)
```

```{r}
Barrow.Co
```

```{r}
BarrowPlantChemistry1$Pb <- as.factor(BarrowPlantChemistry1$Pb)
```

```{r}
Barrow.Pb <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'Pb',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.Pb)
```

```{r}
Barrow.Pb
```

```{r}
BarrowPlantChemistry1$S <- as.factor(BarrowPlantChemistry1$S)
```

```{r}
Barrow.S <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'S',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.S)
```

```{r}
Barrow.S
```

```{r}
BarrowPlantChemistry1$V <- as.factor(BarrowPlantChemistry1$V)
```

```{r}
Barrow.V <- renyicomp(BarrowPlantSpecies1, y=BarrowPlantChemistry1, factor = 'V',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Barrow.V)
```

```{r}
Barrow.V
```

#Load Carnforth or Warton Data#

```{r}
CarnforthPlantChemistry <- read.csv("CarnforthPlantChemistry.csv")
```


```{r}
str(CarnforthPlantChemistry)
```


```{r}
CarnforthPlantSpecies <- read.csv("CarnforthPlantSpecies.csv")
```


```{r}
str(CarnforthPlantSpecies)
```

#Convert data into dataframes for analyses#

```{r}
CarnforthPlantSpecies1 <- data.frame(CarnforthPlantSpecies)
```

```{r}
CarnforthPlantChemistry1 <- data.frame(CarnforthPlantChemistry)
```

#Now to run a series of analyses to assess Renyi biodiversity values for different concentrations of specific elements,
#as well as different pH levels.

```{r}
CarnforthPlantChemistry1$pH <- as.factor(CarnforthPlantChemistry1$pH_level)
```

```{r}
Carnforth.pH <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'pH',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.pH)
```

```{r}
Carnforth.pH
```

```{r}
CarnforthPlantChemistry1$Al2O3 <- as.factor(CarnforthPlantChemistry1$Al2O3)
```

```{r}
Carnforth.Al2O3 <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'Al2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.Al2O3)
```

```{r}
Carnforth.Al2O3
```

```{r}
CarnforthPlantChemistry1$SiO2 <- as.factor(CarnforthPlantChemistry1$SiO2)
```

```{r}
Carnforth.SiO2 <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'SiO2',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.SiO2)
```

```{r}
Carnforth.SiO2
```

```{r}
CarnforthPlantChemistry1$Fe2O3 <- as.factor(CarnforthPlantChemistry1$Fe2O3)
```

```{r}
Carnforth.Fe2O3 <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'Fe2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.Fe2O3)
```

```{r}
Carnforth.Fe2O3
```

```{r}
CarnforthPlantChemistry1$CaO <- as.factor(CarnforthPlantChemistry1$CaO)
```

```{r}
Carnforth.CaO <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'CaO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.CaO)
```

```{r}
Carnforth.CaO
```

```{r}
CarnforthPlantChemistry1$MgO <- as.factor(CarnforthPlantChemistry1$MgO)
```

```{r}
Carnforth.MgO <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'MgO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.MgO)
```

```{r}
Carnforth.MgO
```

```{r}
CarnforthPlantChemistry1$Na2O <- as.factor(CarnforthPlantChemistry1$Na2O)
```

```{r}
Carnforth.Na2O <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'Na2O',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.Na2O)
```

```{r}
Carnforth.Na2O
```

```{r}
CarnforthPlantChemistry1$K2O <- as.factor(CarnforthPlantChemistry1$K2O)
```

```{r}
Carnforth.K2O <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'K2O',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.K2O)
```

```{r}
Carnforth.K2O
```

```{r}
CarnforthPlantChemistry1$Cr2O3 <- as.factor(CarnforthPlantChemistry1$Cr2O3)
```

```{r}
Carnforth.Cr2O3 <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'Cr2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.Cr2O3)
```

```{r}
Carnforth.Cr2O3
```

```{r}
CarnforthPlantChemistry1$TiO2 <- as.factor(CarnforthPlantChemistry1$TiO2)
```

```{r}
Carnforth.TiO2 <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'TiO2',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.TiO2)
```

```{r}
Carnforth.TiO2
```

```{r}
CarnforthPlantChemistry1$MnO <- as.factor(CarnforthPlantChemistry1$MnO)
```

```{r}
Carnforth.MnO <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'MnO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.MnO)
```

```{r}
Carnforth.MnO
```

```{r}
CarnforthPlantChemistry1$P2O5 <- as.factor(CarnforthPlantChemistry1$P2O5)
```

```{r}
Carnforth.P2O5 <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'P2O5',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.P2O5)
```

```{r}
Carnforth.P2O5
```

```{r}
CarnforthPlantChemistry1$SrO <- as.factor(CarnforthPlantChemistry1$SrO)
```

```{r}
Carnforth.SrO <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'SrO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.SrO)
```

```{r}
Carnforth.SrO
```

```{r}
CarnforthPlantChemistry1$BaO <- as.factor(CarnforthPlantChemistry1$BaO)
```

```{r}
Carnforth.BaO <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'BaO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.BaO)
```

```{r}
Carnforth.BaO
```


```{r}
CarnforthPlantChemistry1$As <- as.factor(CarnforthPlantChemistry1$As)
```

```{r}
Carnforth.As <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'As',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.As)
```

```{r}
Carnforth.As
```

```{r}
CarnforthPlantChemistry1$Co <- as.factor(CarnforthPlantChemistry1$Co)
```

```{r}
Carnforth.Co <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'Co',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.Co)
```

```{r}
Carnforth.Co
```

```{r}
CarnforthPlantChemistry1$Pb <- as.factor(CarnforthPlantChemistry1$Pb)
```

```{r}
Carnforth.Pb <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'Pb',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.Pb)
```

```{r}
Carnforth.Pb
```

```{r}
CarnforthPlantChemistry1$S <- as.factor(CarnforthPlantChemistry1$S)
```

```{r}
Carnforth.S <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'S',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.S)
```

```{r}
Carnforth.S
```

```{r}
CarnforthPlantChemistry1$V <- as.factor(CarnforthPlantChemistry1$V)
```

```{r}
Carnforth.V <- renyicomp(CarnforthPlantSpecies1, y=CarnforthPlantChemistry1, factor = 'V',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Carnforth.V)
```

```{r}
Carnforth.V
```

#Loading Hodbarrow Data#

```{r}
HodbarrowPlantSpecies <- read.csv("HodbarrowPlantSpecies.csv")
```


```{r}
str(HodbarrowPlantSpecies)
```


```{r}
HodbarrowPlantChemistry <- read.csv("HodbarrowPlantChemistry.csv")
```


```{r}
str(HodbarrowPlantChemistry)
```

#Converting data to dataframes for analyses#

```{r}
HodbarrowPlantSpecies1 <- data.frame(HodbarrowPlantSpecies)
```


```{r}
HodbarrowPlantChemistry1 <- data.frame(HodbarrowPlantChemistry)
```

#Now to run a series of analyses to assess Renyi biodiversity values for different concentrations of specific elements,
#as well as different pH levels.

```{r}
HodbarrowPlantChemistry1$pH <- as.factor(HodbarrowPlantChemistry1$pH_level)
```


```{r}
Hodbarrow.pH <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'pH_level',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.pH)
```

```{r}
Hodbarrow.pH
```

```{r}
HodbarrowPlantChemistry1$SiO2 <- as.factor(HodbarrowPlantChemistry1$SiO2)
```


```{r}
Hodbarrow.SiO2 <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'SiO2',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.SiO2)
```

```{r}
Hodbarrow.SiO2
```

```{r}
HodbarrowPlantChemistry1$Al2O3 <- as.factor(HodbarrowPlantChemistry1$Al2O3)
```


```{r}
Hodbarrow.Al2O3 <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'Al2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.Al2O3)
```

```{r}
Hodbarrow.Al2O3
```

```{r}
HodbarrowPlantChemistry1$Fe2O3 <- as.factor(HodbarrowPlantChemistry1$Fe2O3)
```


```{r}
Hodbarrow.Fe2O3 <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'Fe2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.Fe2O3)
```

```{r}
Hodbarrow.Fe2O3
```

```{r}
HodbarrowPlantChemistry1$CaO <- as.factor(HodbarrowPlantChemistry1$CaO)
```


```{r}
Hodbarrow.CaO <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'CaO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.CaO)
```

```{r}
Hodbarrow.CaO
```

```{r}
HodbarrowPlantChemistry1$MgO <- as.factor(HodbarrowPlantChemistry1$MgO)
```


```{r}
Hodbarrow.MgO <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'MgO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.MgO)
```

```{r}
Hodbarrow.MgO
```

```{r}
HodbarrowPlantChemistry1$Na2O <- as.factor(HodbarrowPlantChemistry1$Na2O)
```


```{r}
Hodbarrow.Na2O <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'Na2O',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.Na2O)
```

```{r}
Hodbarrow.Na2O
```

```{r}
HodbarrowPlantChemistry1$K2O <- as.factor(HodbarrowPlantChemistry1$K2O)
```


```{r}
Hodbarrow.K2O <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'K2O',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.K2O)
```

```{r}
Hodbarrow.K2O
```

```{r}
HodbarrowPlantChemistry1$Cr2O3 <- as.factor(HodbarrowPlantChemistry1$Cr2O3)
```


```{r}
Hodbarrow.Cr2O3 <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'Cr2O3',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.Cr2O3)
```

```{r}
Hodbarrow.Cr2O3
```

```{r}
HodbarrowPlantChemistry1$TiO2 <- as.factor(HodbarrowPlantChemistry1$TiO2)
```


```{r}
Hodbarrow.TiO2 <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'TiO2',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.TiO2)
```

```{r}
Hodbarrow.TiO2
```

```{r}
HodbarrowPlantChemistry1$MnO <- as.factor(HodbarrowPlantChemistry1$MnO)
```


```{r}
Hodbarrow.MnO <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'MnO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.MnO)
```

```{r}
Hodbarrow.MnO
```

```{r}
HodbarrowPlantChemistry1$P2O5 <- as.factor(HodbarrowPlantChemistry1$P2O5)
```


```{r}
Hodbarrow.P2O5 <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'P2O5',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.P2O5)
```

```{r}
Hodbarrow.P2O5
```

```{r}
HodbarrowPlantChemistry1$SrO <- as.factor(HodbarrowPlantChemistry1$SrO)
```


```{r}
Hodbarrow.SrO <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'SrO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.SrO)
```

```{r}
Hodbarrow.SrO
```

```{r}
HodbarrowPlantChemistry1$BaO <- as.factor(HodbarrowPlantChemistry1$BaO)
```


```{r}
Hodbarrow.BaO <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'BaO',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.BaO)
```

```{r}
Hodbarrow.BaO
```

```{r}
HodbarrowPlantChemistry1$As <- as.factor(HodbarrowPlantChemistry1$As)
```


```{r}
Hodbarrow.As <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'As',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.As)
```

```{r}
Hodbarrow.As
```

```{r}
HodbarrowPlantChemistry1$Co <- as.factor(HodbarrowPlantChemistry1$Co)
```


```{r}
Hodbarrow.Co <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'Co',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.Co)
```

```{r}
Hodbarrow.Co
```

```{r}
HodbarrowPlantChemistry1$Pb <- as.factor(HodbarrowPlantChemistry1$Pb)
```


```{r}
Hodbarrow.Pb <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'Pb',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.Pb)
```

```{r}
Hodbarrow.Pb
```

```{r}
HodbarrowPlantChemistry1$S <- as.factor(HodbarrowPlantChemistry1$S)
```


```{r}
Hodbarrow.S <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'S',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.S)
```

```{r}
Hodbarrow.S
```

```{r}
HodbarrowPlantChemistry1$V <- as.factor(HodbarrowPlantChemistry1$V)
```


```{r}
Hodbarrow.V <- renyicomp(HodbarrowPlantSpecies1, y=HodbarrowPlantChemistry1, factor = 'V',
scales=c(0, 0.25, 0.5, 1, 2, 4, 8, Inf), permutations=100, plotit=F)
```

```{r}
summary(Hodbarrow.V)
```

```{r}
Hodbarrow.V
```
